---
title: "Portfolio5"
author: "Lauren"
date: "4/9/2021"
output: html_document
---


The purpose of this portfolio piece is to come up with a list (CSV file) of apartments in a particular price range, by pulling apartments names, addresses, and rent from apartments.com

1. Load packages
```{r setup}

library(tidyverse) 
library(skimr)
library(rvest)
library(robotstxt)

```

2. Check permission
```{r check.permission}

paths_allowed("https://www.apartments.com/winston-salem-nc/?gclid=CjwKCAjw9r-DBhBxEiwA9qYUparLtarTAGWxsU9elNTmtbJu4Pge97m0TxH_S0fbbqjiEzCl-3wRBBoC9z0QAvD_BwE&gclsrc=aw.ds")
```

3. Collect title, rent, and address info. For some reason when I scraped address R pulled a bunch of strings ("\r\n...) so I'm just filtering all of those out 
```{r pull.apartment.info}
page <- read_html ("https://www.apartments.com/winston-salem-nc/?gclid=CjwKCAjw9r-DBhBxEiwA9qYUparLtarTAGWxsU9elNTmtbJu4Pge97m0TxH_S0fbbqjiEzCl-3wRBBoC9z0QAvD_BwE&gclsrc=aw.ds")

titles <- page %>% 
  html_nodes(".title") %>% 
  html_text()


rent <- page %>% 
  html_nodes(".price-range") %>% 
  html_text()

address <- page %>% 
  html_nodes(".js-url") %>% 
  html_text()

apartments <- tibble(address = address)

apartments <- apartments %>% 
  filter(address != "\r\n                        \r\n                            \r\n                        \r\n                    ")

apartments

```


4. Combine apartments name, rent, and address into one data frame
``` {r create.tibble}

apartments <- apartments %>% 
  mutate(rent = rent)

apartments <- apartments %>% 
  mutate(name = titles)

as.data.frame(apartments)

```

5. Save the data frame as a CSV so I can use it during my apartment searching
```{r write.csv}

write.csv(apartments, "apartments.csv")

```